%% ----------------------------------------------------------------
%% Methods.tex
%% ---------------------------------------------------------------- 
\chapter{Methods} \label{Chapter: Methods}

Parameters are defined in Results (not in Methods)

It doesn't matter if you don't include all the methods, only the ones for the final results.

Check that you provide enough background information: your reader does not know what you know. Assuming that your reader knows much more than you and therefore omitting background information is a very common problem with students. A typical example would be a Methods section that directly launches into what you have done without first telling why. Although it is evident to you that to get from A to B you need to do X, this is probably far less obvious to the reader. If you only tell the reader that you did X, she is confused. Why did you do X? Never assume that the reader knows your motivation, or the details of every method you used, or why your research question is important. Tell her.

Plagiarism: use of code (this includes open source code!) that was not written by you, without acknowledgement of the source

Check that the reader can replicate your results. Verify that your Methods section (and the supplementary sections if any) contains everything that the reader needs to know. Also check that you provide links to your code and your data if it can be released without violating anyone’s privacy.

\begin{enumerate}
\item How am I going to measure it?
\item How am I going to prove it?
\end{enumerate}
